---
title: "Introduction to Policy Learning Under Constraint R-package (PLUCR)"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PLUCR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,        # show code
  message = TRUE,     # show messages from code
  warning = TRUE      # show warnings from code
)
```

# 1. Introduction

The `PLUCR` package provides tools for estimating treatment probabilities that maximize a primary clinical outcome while controlling for the occurrence of adverse events. This dual-objective framework is particularly relevant in medical or decision-making settings where benefits must be balanced against potential harms.

Many existing methods derive treatment policies based on the sign of the Conditional Average Treatment Effect (CATE). In this setup, individuals with a positive CATE are assigned treatment, as it is expected to be beneficial; those with a non-positive CATE are not treated. While effective in simple settings, this strategy becomes inadequate when multiple outcomes must be considered, particularly when adverse events are ignored.

`PLUCR` addresses this limitation by framing the policy learning task as a constrained optimization problem. The goal is to learn a probability that not only improves the primary outcome but also respects pre-specified constraints on adverse effects. The method implemented in `PLUCR` estimates treatment probabilities by adapting the Conditional Average Treatment Effect (CATE) to ensure compliance with a predefined constraint on adverse events. This is achieved through an iterative procedure that alternates between optimizing the policy and correcting its estimator, ultimately leading to a constrained-optimal policy.

# 2. Getting started 

This section demonstrates a basic example of how to use the `PLUCR` package. We begin by generating a synthetic data set and applying the main function, `main_algorithm()`, to learn an optimal policy under adverse event constraints.

## 2.1. Installation

You can install the development version from your local source:

```{r,eval=FALSE}
devtools::install_github("laufuentes/PLUCR")
```

## 2.2. Load required packages and data
```{r, eval=FALSE}
library(PLUCR)
library(SuperLearner)
library(grf)
library(dplyr)
library(tidyr)
library(ggplot2)
```

We generate synthetic observational data using the built-in `generate_data()` function. This function also produces the complete data structure (which is typically unavailable in real-world applications and used here for evaluation purposes only) as well as the oracular treatment effect functions `delta_mu()` and `delta_nu()`.

```{r, eval=FALSE}
n <- 3000  # Sample size
ncov <- 10L # Number of covariates
scenario_mu <- "Threshold"
scenario_nu <- "Threshold"

# Generate synthetic scenario
exp <- PLUCR::generate_data(n, 
                            ncov, 
                            scenario_mu = scenario_mu, 
                            scenario_nu = scenario_nu, 
                            seed=2025) 

# # Complete data (not available in real settings)
df_complete <- exp[[1]] 

# # Observational data (to be used for training)
df_obs <- exp[[2]]

# # Oracular delta mu function (treatment effect over Y conditionned on X) 
delta_mu <- exp[[3]]

# # Oracular delta mu function (treatment effect over Y conditionned on X) 
delta_nu <- exp[[4]]
```

## 2.3. Prepare Variables and Function parameters

In this step, we extract the necessary variables from the observational data set and define the parameters required by the `main_algorithm()` function. This includes specifying the covariates, treatment indicator, outcomes, and adverse events.

```{r,eval=FALSE}
# Covariates matrix 
X <- df_obs %>%
  dplyr::select(starts_with("X."))%>%
  as.matrix()

# Binary treatment assignment (0 = control, 1 = treated)
A <- df_obs$Treatment

# Primary outcome, assumed to be scaled to [0, 1]
Y <- df_obs$Y

# Binary indicator of adverse events (0=No adverse event, 1=adverse event)
Xi <- df_obs$Xi
```

We now define the parameters to be passed to `main_algorithm()`. These include the learners used in `SuperLearner` estimation, the directory for saving results, and tuning parameters that control constraint enforcement and optimization precision.

```{r, eval=FALSE}
# SuperLearner library used for estimating nuisance functions
# You can customize this list. The default includes:
# - SL.mean: simple mean predictor
# - SL.glm: generalized linear model
# - SL.ranger: random forest
# - SL.grf: generalized random forest
# - SL.xgboost: gradient boosting
SL.library <- c("SL.mean", "SL.glm", "SL.ranger", "SL.grf", "SL.xgboost")

# Insert a root directory where output files, results and images will be saved
root.path <- "./results"

# An increasing sequence of non-negative numeric scalars controlling 
# the penalty for violating the constraint (seq(1,8, by=1) by default).
Lambda_candidates <- seq(1, 10, by=1)

# A vector of non-negative scalars controlling the sharpness of the 
# treatment probability function (c(0.05, 0.1, 0.25, 0.5) by default)
Beta_candidates <- c(0.05, 0.1, 0.25, 0.5)

# Constraint tolerance (alpha): maximum allowed increase in adverse event risk
# Example: 0.2 means the policy may increase adverse event probability by up to 20%
alpha.tolerance <- 0.2

# Optimization precision: Controls the granularity of the policy search.
# Smaller values lead to finer approximations but require more computation (default is 0.025).
# For a quick toy example, you may prefer using 0.05 instead.
optimization.precision <- 0.025 

# Parameter indicating whether to center the treatment policy to ensure that 
# probability of treatment assignment for null treatment effect is 0.5. 
centered <- FALSE
```

## 2.4. Run the main algorithm 
With all variables and parameters defined, we now apply the `main_algorithm()` from the `PLUCR` package. This function executes the full estimation pipeline, consisting of the following steps:

1- Estimation of nuisance components using the `SuperLearner` ensemble framework

2- Learning a treatment policy that maximizes the estimated policy value while enforcing the estimated constraint on the probability of adverse events. This is accomplished through an alternating optimization procedure that corrects the baseline estimator of the objective function.

The output of this procedure includes:

- An unconstrained policy, which aims solely to maximize the policy value without accounting for potential adverse events.

-A constrained-optimal policy, which achieves optimality while satisfying the pre-specified constraint on the expected rate of adverse events.
```{r, eval=FALSE}
output <- PLUCR::main_algorithm(X=X, A=A, Y=Y, Xi=Xi, 
                                Lambdas = Lambda_candidates,
                                alpha=alpha.tolerance, 
                                B= Beta_candidates, 
                                precision=optimization.precision,
                                centered=centered,
                                SL.library = SL.library, 
                                root.path=root.path)

if(is.list(output)){
  theta_0 <- output[[1]]
  theta_final <- output[[2]]
}else{
  theta_final <- output
}
```

The main function returns a list of matrices (`theta_0` and `theta_final`), or `theta_0` alone. These matrices are used to construct the optimal treatment rule in two steps, as follows:

```{r, eval=FALSE}
# First, build `psi` using the `make_psi` function and evaluate it at `X` (i.e., `psi(X)`). 
psi_final <- PLUCR::make_psi(theta_final)

# Obtain the optimal treatment rule by applying `sigma_beta` to the optimal `beta` associated to `theta_final`
optimal_treatment_probability <- PLUCR::sigma_beta(psi_final(X), beta=attr(theta_final, "beta"))
```

## 2.5. Other results 
### 2.5.1. Naive approach 

As an alternative, we can apply the `naive_approach_algorithm`, which relies on baseline nuisance parameter estimators and omits the correction step implemented in `main_algorithm()`. This function assumes that the nuisance components—specifically the outcome regression, the adverse event regression and the propensity score model, have already been estimated and saved in their respective folders (`Mu.hat`, `Nu.hat`, `PS.hat`). 

Using these pre-computed components, the algorithm directly learns a treatment policy that, maximizes the estimated policy value, and enforces the estimated constraint on the probability of adverse events, using the baseline nuisance estimates.


The output includes:

- An unconstrained policy, which maximizes the primary outcome without regard to adverse events.

- A constrained-optimal policy, which satisfies the specified constraint on adverse event probability using the uncorrected nuisance estimators.
```{r, eval=FALSE}
# Load pre-required parameters, computed on previous algorithm 

# Folds for splitting data 
folds <- readRDS(file.path(root.path,"Folds","folds.rds")) 
# Primary outcome model
mu.hat.nj <- readRDS(file.path(root.path,"Mu.hat","mu.hat.nj.rds")) 
# Adverse event model
nu.hat.nj <- readRDS(file.path(root.path,"Nu.hat","nu.hat.nj.rds")) 
# Propensity score model 
ps.hat.nj <- readRDS(file.path(root.path,"PS.hat","ps.hat.nj.rds"))
  
# Split data into training and testing set
# The training set will be used to train the treatment rule
X_train <- X[folds[[2]],]
A_train <- A[folds[[2]]]
Y_train <- Y[folds[[2]]]
Xi_train <- Xi[folds[[2]]]
# The test set will be used exclusively for policy evaluation. 
X_test <- X[folds[[3]],]
A_test <- A[folds[[3]]]
Y_test <- Y[folds[[3]]]
Xi_test <- Xi[folds[[3]]]

# Split the previous nuisances into training and testing set
mu0_train <- function(a,x){mu.hat.nj(a=a,x=x,ff=1)}
nu0_train <- function(a,x){nu.hat.nj(a=a,x=x,ff=1)}
prop_score_train <- function(a,x){ps.hat.nj(a,x,1)}

mu0_test <- function(a,x){mu.hat.nj(a,x,3)}
nu0_test <- function(a,x){nu.hat.nj(a,x,3)}
prop_score_test <- function(a,x){ps.hat.nj(a,x,3)}

# Run the naive approach algorithm 
naive_output <- naive_approach_algorithm(X, A, Y, Xi, folds, 
                                         mu0_train, mu0_test, 
                                         nu0_train, nu0_test, 
                                         prop_score_train, prop_score_test, 
                                         alpha = alpha.tolerance, 
                                         centered=centered,
                                         precision=optimization.precision,
                                         root.path = root.path)

if(is.list(naive_output)){
 theta_naive <- naive_output[[2]] 
}else{
  theta_naive <- naive_output[[1]]
}
# Evaluate the optimal treatment rule according to the naive approach
eval_naive <- process_results(theta=theta_naive, X=X_test, A=A_test, Y=Y_test, Xi=Xi_test, 
                              mu0=mu0_test, nu0=nu0_test, prop_score=prop_score_test, 
                              lambda = attr(theta_naive, "lambda"), alpha = alpha.tolerance,
                              beta= attr(theta_naive, "beta"))[[1]]
```

### 2.5.2. Oracular results

In this illustrative setting, we operate under a controlled, simulated environment in which the true data-generating mechanisms, denoted by `delta_mu` (for the primary outcome) and `delta_nu` (for the adverse event process), are fully known. This allows us to implement an oracular benchmark using the `oracular_approach_algorithm`.

Unlike real-world applications, where these nuisance components must be estimated from data, the oracular approach bypasses this step and leverages the known functions directly. As such, it provides a useful reference point for evaluating the performance of data-driven methods. The algorithm computes a treatment policy that maximizes the expected primary outcome, and satisfies a constraint on the expected rate of adverse events, based on the true underlying mechanisms. 

The output includes:

- An unconstrained optimal policy, derived solely from the objective of maximizing the primary outcome.

- A constrained-optimal policy, which enforces the specified constraint on adverse event probability using the known functions.

This approach serves as a theoretical upper bound on performance and offers a meaningful benchmark for assessing the quality of both the naïve and corrected estimators presented earlier.

```{r, eval=FALSE}
oracular_output <- oracular_approach_algorithm(X=X, A=A, Y=Y, Xi=Xi, 
                                               folds=folds,
                                               delta_Mu=delta_mu, delta_Nu= delta_nu, 
                                               alpha = alpha.tolerance, centered=centered,
                                               precision = optimization.precision, 
                                               scenario_mu=scenario_mu, scenario_nu=scenario_nu, 
                                               root.path = root.path)

if(is.list(oracular_output)){
 theta_oracular <- oracular_output[[2]] 
}else{
  theta_oracular <- oracular_output[[1]]
}
eval_oracular <- oracular_process_results(theta=theta_oracular, X=X_test,  
                                          delta_Mu = delta_mu, delta_Nu = delta_nu, 
                                          scenario_mu = scenario_mu, 
                                          scenario_nu = scenario_nu, 
                                          lambda = attr(theta_oracular, "lambda"), 
                                          alpha = alpha.tolerance, 
                                          beta= attr(theta_oracular, "beta"))
```

# 3. Play with results 

The function `synthetic_data_plot()` function provides an initial visualization of the treatment effects for both the primary outcome and the adverse event across the covariate space.

```{r, eval=FALSE}
fig <- PLUCR::synthetic_data_plot(delta_Mu=delta_mu, 
                                  delta_Nu=delta_nu, 
                                  root.path=root.path, 
                                  name=paste0(scenario_mu,"-", scenario_nu))

print(fig)
```

In addition, we can visualize the learned treatment policies by plotting treatment probabilities against selected covariates that allow for meaningful two-dimensional representation, using the function `visual_treatment_plot`. 

```{r, eval=FALSE}
if(is.list(output)){
 PLUCR::visual_treatment_plot(make_psi(theta_0)(X), 
                              lambda = attr(theta_0, "lambda"), 
                              beta = attr(theta_0, "beta"), 
                              centered = centered, 
                              Var_X_axis = df_obs$X.1, Var_Y_axis = df_obs$X.2,
                              root.path = root.path, name = "Initial") 
}

 PLUCR::visual_treatment_plot(make_psi(theta_naive)(X), 
                              lambda = attr(theta_naive, "lambda"), 
                              beta = attr(theta_naive, "beta"), 
                              centered = centered, 
                              Var_X_axis = df_obs$X.1, Var_Y_axis = df_obs$X.2,
                              root.path = root.path, name = "Naive")
 
 PLUCR::visual_treatment_plot(make_psi(theta_final)(X), 
                              lambda = attr(theta_final, "lambda"), 
                              beta = attr(theta_final, "beta"), 
                              centered = centered, 
                              Var_X_axis = df_obs$X.1, Var_Y_axis = df_obs$X.2,
                              root.path = root.path, name = "Final")
 
 PLUCR::visual_treatment_plot(make_psi(theta_oracular)(X), 
                              lambda = attr(theta_oracular, "lambda"), 
                              beta = attr(theta_oracular, "beta"), 
                              centered = centered, 
                              Var_X_axis = df_obs$X.1, Var_Y_axis = df_obs$X.2,
                              root.path = root.path, name = "Oracular")
```

Finally, we compare treatment recommendations across approaches by evaluating their estimated policy values and associated constraint violations.

```{r, eval=FALSE}
eval_0 <- process_results(theta_0, X_test, A_test, Y_test, Xi_test, mu0_test, nu0_test, prop_score_test, lambda=attr(theta_0, "lambda"), alpha.tolerance,  beta=attr(theta_0, "beta"), centered)[[1]]

eval_final <- readRDS(file.path(root.path, "Evaluation", 
                                paste0(attr(theta_final, "beta"), "_", 
                                       attr(theta_final, "lambda"), ".rds")))


if(is.list(output)){
  data <- tibble(
  method = c("Theta_0", "Theta_naive", "Theta_final", "Theta_oracular"),
  policy_value = c(eval_0$policy_value, 
                   eval_naive$policy_value, 
                   eval_final$policy_value, 
                   eval_oracular$policy_value),
  constraint = c(eval_0$constraint, 
                 eval_naive$constraint, 
                 eval_final$constraint, 
                 eval_oracular$constraint))
}else{
  data <- tibble(
  method = c("Theta_naive", "Theta_final", "Theta_oracular"),
  policy_value = c(eval_naive$policy_value, 
                   eval_final$policy_value, 
                   eval_oracular$policy_value),
  constraint = c(eval_naive$constraint, 
                 eval_final$constraint, 
                 eval_oracular$constraint))
}

# Call the function
plot_metric_comparison(data, metrics = select(data, -"method") %>% colnames(), 
                       techniques = data$method, root.path = root.path)
```

In a simulated setting where the true data-generating mechanisms are known, we can evaluate the oracle performance of each parameter value, `theta_naive`, `theta_0`, and `theta_final`, by computing their corresponding outcomes using the `oracular_process_results()` function, as demonstrated for `theta_oracular`.
 

Several binary treatment decisions can be derived from a single treatment probability recommendation. For instance, one may draw individual treatment assignments from a Bernoulli distribution with conditional mean given by the learned treatment probabilities. Alternatively, a decision threshold can be introduced, above which patients are assigned treatment and below which they are not. 

# Appendix. Understanding the Algorithm Internally

The `main_algorithm()` function is designed to abstract away the technical details while still allowing flexibility through its parameters. Internally, it carries out a constrained policy learning procedure, broken down into three main stages, each performed on a different fold. 

## Preliminary Step: Data Checks and Cross-Fitting Folds
Before estimating nuisance functions and optimizing the policy, the algorithm performs three important preliminary tasks:

- Creates the folds where results will be saved. 

- Verifies that the input variables (X, A, Y and Xi) meet the required format and assumptions, such as outcome ranges, binary treatment/adverse event values.

- Creates 3 cross-validation folds to enable cross-fitting. 
```{r, eval=FALSE}
 n <- nrow(X)
  # Folds for cross-validation 
  folds <- SuperLearner::CVFolds(n, 
                                 id = NULL,
                                 Y = Y,
                                 cvControl = SuperLearner::SuperLearner.CV.control(V = Jfold, 
                                                                                   shuffle = TRUE))
  saveRDS(folds, file=file.path(root.path,"Folds","folds.rds")) 
  checks<- PLUCR::check_data(Y, Xi, A, X, folds)
```

## Step 1: Estimate and Save Nuisance Parameters

Once the variables have been validated and the cross-fitting folds are defined, the algorithm proceeds to estimate the nuisance parameters. These models are each trained using the pre-defined folds to enable cross-fitting, which improves robustness and reduces overfitting.

The key nuisance parameters estimated are:

- **Primary outcome model:** $E[Y \mid A, X]$  
- **Adverse event model:** $E[\xi \mid A, X]$  
- **Propensity score model:** $P[A \mid X]$  

Each model is fit separately and the estimates are saved for later use in policy learning.

```{r, eval=FALSE}
# Estimate primary outcome model E[Y | A, X]
mu.hat.nj <- PLUCR::estimate_mu(
  Y = Y, A = A, X = X, folds = folds,
  SL.library = SL.library, V = 2L
)
saveRDS(mu.hat.nj, file = file.path(root.path, "Mu.hat", "mu.hat.nj.rds"))

# Estimate adverse event model E[Xi | A, X]
nu.hat.nj <- PLUCR::estimate_nu(
  Xi = Xi, A = A, X = X, folds = folds,
  SL.library = SL.library, V = 2L
)
saveRDS(nu.hat.nj, file = file.path(root.path, "Nu.hat", "nu.hat.nj.rds"))

# Estimate propensity score model P[A | X]
ps.hat.nj <- PLUCR::estimate_ps(
  A = A, X = X, folds = folds,
  SL.library = SL.library, V = 2L
)
saveRDS(ps.hat.nj, file = file.path(root.path, "PS.hat", "ps.hat.nj.rds"))
```

After estimating the nuisance parameters, the next step is to organize the data into **training** and **testing** sets. This allows us to:

- Learn nuisance components on a first training subset of the data. 
- Estimate the optimal treatment policy on a second independent training set of the data.
- Evaluate the learned policy’s performance on an independent test set.

```{r, eval=FALSE}
# Training functions & data (first and second folds)
# functions (first fold)
mu0_train <- function(a,x){mu.hat.nj(a=a,x=x,ff=1)}
nu0_train <- function(a,x){nu.hat.nj(a=a,x=x,ff=1)}
prop_score_train <- function(a,x){ps.hat.nj(a,x,1)}

# data (second fold)
X_train <- X[folds[[2]],]
A_train <- A[folds[[2]]]
Y_train <- Y[folds[[2]]]
Xi_train <- Xi[folds[[2]]]
  

# Testing functions & data (third fold)
# functions
mu0_test <- function(a,x){mu.hat.nj(a,x,3)}
nu0_test <- function(a,x){nu.hat.nj(a,x,3)}
prop_score_test <- function(a,x){ps.hat.nj(a,x,3)}

# data (third fold)
X_test <- X[folds[[3]],]
A_test <- A[folds[[3]]]
Y_test <- Y[folds[[3]]]
Xi_test <- Xi[folds[[3]]]
```

## Step 2: Policy optimization

In this step, we run the core algorithm of the `PLUCR` package — the **alternating optimization procedure** implemented in the `Optimization_Estimation()` function. This procedure learns an optimal treatment policy that maximizes the expected primary outcome while controlling the probability of adverse events.

The procedure is executed over a grid of $(\lambda, \beta)$ values, where:

- $\lambda$ controls the trade-off between maximizing the primary outcome and satisfying the constraint.
- $\beta$ is a tuning parameter influencing the optimization regularization.

Before evaluating the entire grid, the algorithm first solves the problem with $\lambda = 0$ in order to check whether the unconstrained optimal policy already satisfies the constraint. If it does, no further optimization over the grid is necessary.


During the search over $\lambda$, once the constraint is satisfied for the first time, the procedure saves the corresponding results at each $\beta$ value. The search over $\lambda$ then stops when the upper bound of the confidence interval for the constraint value drops below zero.

**Alternating Optimization Procedure**

Whether with $\lambda = 0$ or $\lambda > 0$, the procedure iterates as follows:

1. Initial estimation of the plug-in objective function $L(\psi)$ using $\Delta\mu_n^k$ and $\Delta\nu_n^k$ derived from, 
   - $\mu_n^k$: the expected outcome model (for k=0, this corresponds to `mu0_train`).
   - $\nu_n^k$: the adverse event model (for k=0, this corresponds to `nu0_train`).

2. **Policy optimization**: Frank- Wolfe algorithm 
   Minimize $L^k_n(\psi)$ to obtain a new candidate policy $\psi_k$.

3. **Update nuisance parameters**:
   - Estimate $\epsilon_1$ and $\epsilon_2$ to correct the outcome and adverse event models using all previous solutions $(\psi_0, ..., \psi_k)$, yielding updated models  $\mu_n^{k+1}$, $\nu_n^{k+1}$ (using functions `update_mu_XA`, `update_nu_XA`).

4. Repeat until convergence or until the maximum number of iterations is reached.
```{r, eval=FALSE}
# Start by testing the unconstrained case with lambda = 0
saved <- FALSE  # Flag to track whether a valid result has already been saved
combinations <- NULL  # Matrix to store (beta, lambda) pairs that satisfy the constraint
beta_0 <- NULL  # Arbitrary beta value since constraint is not evaluated yet
lambda <- 0

# Run optimization with lambda = 0 (no constraint)
out <- PLUCR::Optimization_Estimation(mu0=mu0_train, nu0=nu0_train, 
                                      prop_score=prop_score_train, 
                                      X=X_train, A=A_train, Y=Y_train, Xi=Xi_train, 
                                      lambda=0, alpha=alpha, precision=precision, beta=0.05,
                                      centered=centered, tol=tol, max_iter=max_iter)

# Extract the final policy from the iteration  
theta_0 <- out$theta_collection[[length(out$theta_collection)]]
attr(theta_0, "lambda") <- 0  # Save the lambda as an attribute 

# Evaluate the policy on the test data for all possible betas
for (beta in B){
    res_0 <- process_results(theta_0, X_test, A_test, Y_test, Xi_test, 
                             mu0_test, nu0_test, prop_score_test, lambda=0, 
                             alpha,  beta, centered)
    # Loop to check constraint satisfaction
    if (res_0[[1]]$constraint < 0) {
      min_constraint_lambda0 <- res_0[[1]]$constraint
      
      if (res_0[[1]]$lwr_bound_policy_value > max_policy_value) {
        beta_0 <- beta
        max_policy_value <- res_0[[1]]$lwr_bound_policy_value
        saveRDS(theta_0, file = file.path(root.path, "Theta_opt", paste0(beta, "_", 0, ".rds")))
         attr(theta_0, "lambda") <- lambda
          attr(theta_0, "beta") <- beta
        saveRDS(out, file=file.path(root.path,"Intermediate",paste0(beta,"_",0,".rds")))
        saveRDS(res_0[[1]], file=file.path(root.path,"Evaluation",paste0(beta,"_",0,".rds")))
        combinations <- rbind(combinations, c(beta_0, 0))
        saved <- TRUE}
    }else{
      if(res_0[[1]]$constraint<min_constraint_lambda0){
        min_constraint_lambda0 <- res_0[[1]]$constraint
        beta_0 <- beta
      }
  }
    if(res_0[[2]]<0){
      warning(sprintf(paste("The constraint was already satisfied for lambda=0.")))
      attr(theta_0, "beta") <- beta_0
      return(theta_0)
    }
  }
  attr(theta_0, "beta") <- beta_0 # Save the beta as an attribute 

  # Begin training over the grid: find for each beta value the optimal lambda
 for (beta in B){
      saved <- FALSE
      for (lambda in Lambdas){
       # Run alternated procedure for each beta and lambda combination 
         out <- PLUCR::Optimization_Estimation(mu0=mu0_train, nu0=nu0_train, 
                                               prop_score=prop_score_train, 
                                               X=X_train, A=A_train, Y=Y_train, Xi=Xi_train, 
                                               lambda=lambda, alpha=alpha, precision=precision, 
                                               beta=beta, centered=centered, 
                                               tol=tol, max_iter=max_iter)
        # Extract final policy
        theta_opt <- out$theta_collection[[length(out$theta_collection)]]
        ### Evaluating 
        res <- process_results(theta_opt, X_test, A_test, Y_test, Xi_test, 
                               mu0_test, nu0_test, prop_score_test, lambda, 
                               alpha,  beta, centered)
        if (!saved && res[[1]]$constraint < 0) {
          saveRDS(res[[1]], file=file.path(root.path,"Evaluation", 
                                           paste0(beta, "_", lambda,".rds")))
          saveRDS(out, file=file.path(root.path,"Intermediate",
                                      paste0(beta,"_",lambda,".rds")))
          saveRDS(theta_opt, file = file.path(root.path, "Theta_opt", 
                                              paste0(beta, "_", lambda, ".rds")))
          attr(theta_opt, "lambda") <- lambda
          attr(theta_opt, "beta") <- beta
          saved <- TRUE
          combinations <- rbind(combinations, c(beta, lambda))
        }
        # Stop search if constraint's upper CI bound is negative
        if(res[[2]]<0){
          break
        }
      }
 }
# Select the optimal combination (beta, lambda)
files_del <- file.path(root.path,"Intermediate")
unlink(files_del, recursive = TRUE)
  
# Select the optimal combination (beta, lambda)
optimal_combination <- get_opt_beta_lambda(combinations,root.path)
beta <- optimal_combination$beta
lambda <- optimal_combination$lambda
theta_keep <- paste0(beta, "_", lambda, ".rds")

# Delete unwanted files in Theta_opt
theta_files <- list.files(file.path(root.path, "Theta_opt"))
theta_to_delete <- theta_files[basename(theta_files) != theta_keep]
file.remove(file.path(root.path,"Theta_opt",theta_to_delete))

# Delete unwanted files in Evaluation
eval_files <- list.files(file.path(root.path, "Evaluation"))
eval_to_delete <- eval_files[basename(eval_files) != theta_keep]
file.remove(file.path(root.path,"Evaluation", eval_to_delete))

# Load the corresponding theta for the optimal (beta, lambda) combination
theta_final <- readRDS(file = file.path(root.path, "Theta_opt", 
                                            paste0(optimal_combination$beta, "_",
                                                   optimal_combination$lambda, ".rds"))) 
# Save the optimal combiation (lambda, beta) as an attribute 
attr(theta_final, "lambda") <- optimal_combination$lambda 
attr(theta_final, "beta") <- optimal_combination$beta
    
# Compute the optimal treatment probabilities with sigma_beta
psi_values <- make_psi(theta_final)(X_test)
optimal_treatment_rule <- sigma_beta(psi_values, beta = attr(theta_final, "beta"))
    
# Calculate proportion over 0.5 and warn the user if the treatment probabilities are too low.
prop_over_0.50 <- mean(optimal_treatment_rule > 0.5)
if(prop_over_0.50<0.1){
  warning(sprintf(
        paste("Only %.1f%% of the test set has an optimal treatment probability above 0.5.",
          "This may indicate that your tolerance for adverse events (alpha) is too strict.",
          "Consider relaxing it if treatment is being under-assigned."), 100 * prop_over_0.50))
}
  
print(list(theta_0, theta_final))
```

